Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2020-01-08 ms.tex
dynamic spectra from OTIS test
fixing up dynamic spectrum
further updates to dynamic spectrum image, also including spec pipeline fixes
plotting representative spectrum and broadband time series

>>>>

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{o9LEDwFlat_dyn_spec_NRCN83-256-O9LW.pdf}{0.79\textwidth}{Dynamic Spectrum}}
\gridline{\fig{o9LEDwFlat_ind_spec_NRCN83-256-O9LW.pdf}{0.49\textwidth}{Representative Spectrum}
\fig{o9LEDwFlat_bb_series_NRCN83-256-O9LW.pdf}{0.49\textwidth}{Broadband Time Series}}
\caption{Dynamic spectrum with grism on the LW channel.
}\label{fig:otisLWdynSpec}
\end{figure*}
